---
title: "R Project 1 - Hello R"
author: "Skylar B Burris"
date: "1/23/2020"
output: 
  html_document: 
    fig_height: 14
    fig_width: 10
    highlight: tango
    theme: journal
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

_This has 1846 rows, but it does not give you the number of columns. (But, if you scroll down to the bottom of the instructions sheet you see table with 3 columns). The variables included in the data frame are 'dataset', 'x', and 'y'._

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


Second, let's plot the data in the star dataset:

```{r plot-star, fig.height=5, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

_This value is differnet to the r of dino by .0015._

### Exercise 4

Third, let's plot the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

_This value is differnet to the r of dino by .0038._


### Exercise 5

Finally, let's plot the data in the facetting dataset:

```{r plot-facetting, fig.height=9, fig.width=9}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

And next generate all the summary correlation coefficients:

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
